\textbf{EECS 340: Assignment 3}

### 2020-02-21 assignment_3/article.tex
🔨 Update Question 4(1) with explanatory comments.

\begin{algorithm}
\caption{QuickMiss(C, D, p, r, missLeft)}\label{QuickMiss}
    \begin{algorithmic}[1]
        \Procedure{QuickMiss}{C, D, p, r, missLeft}
        \If {$p < r$}
            \State $q \gets \textsc{Partition}(C, p, r)$
            \If {$C[q] == D[q]$}
                \State \Return $\textsc{QuickMiss}(C, D, q+1, r, False)$
            \Else
                \State \Return $\textsc{QuickMiss}(C, D, p, q-1, True)$
            \EndIf
        \EndIf
        \If {$missLeft == True$}
            \State \Return $D[p]$
        \Else
            \State \Return $D[r+1]$
        \EndIf
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Partition(A, p, r)}\label{Partition}
    \begin{algorithmic}[1]
        \Procedure{Partition}{A, p, r}
        \State $q \gets p$
        \For {$i \gets p$ \textbf{to} $r$}
            \If {$\textsc{Compare-Strings}(A[i], A[r])$}
                \State $\textsc{Swap}(A[i], A[q])$ \Comment{Exchange two elements.}
                \State $q \gets q+1$
            \EndIf
        \EndFor
        \State $\textsc{Swap}(A[q], A[r])$
        \State \Return $q$
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}
\caption{QuickMiss(C, D, p, r, missLeft)}\label{QuickMiss}
    \begin{algorithmic}[1]
        \Procedure{QuickMiss}{C, D, p, r, missLeft} \Comment{Set any value to $missLeft$ for initial call.}
        \If {$p < r$} \Comment{Base case, terminates when $p = r$.}
            \State $q \gets \textsc{Partition}(C, p, r)$ \Comment{Get pivot index from inclusive $C[p, r]$.}
            \If {$C[q] == D[q]$} \Comment{If no missing element on left portion to $q$.}
                \State \Return $\textsc{QuickMiss}(C, D, q+1, r, False)$ \Comment{Thus check right partition.}
            \Else \Comment{If no missing element on right portion to $q$.}
                \State \Return $\textsc{QuickMiss}(C, D, p, q-1, True)$ \Comment{Thus check left partition.}
            \EndIf
        \EndIf
        \If {$missLeft == True$}
            \State \Return $D[p]$ \Comment{Missing element index within range of $C$, simply return.}
        \Else
            \State \Return $D[r+1]$ \Comment{Missing element $> r$, $+1$ to retrive from $D$.}
        \EndIf
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Partition(A, p, r)}\label{Partition}
    \begin{algorithmic}[1]
        \Procedure{Partition}{A, p, r}
        \State $q \gets p$
        \For {$i \gets p$ \textbf{to} $r$}
            \If {$\textsc{Compare-Strings}(A[i], A[r])$} \Comment{if $A[i] < A[r]$ alphabetically.}
                \State $\textsc{Swap}(A[i], A[q])$ \Comment{Exchange two elements.}
                \State $q \gets q+1$
            \EndIf
        \EndFor
        \State $\textsc{Swap}(A[q], A[r])$
        \State \Return $q$
        \EndProcedure
    \end{algorithmic}
\end{algorithm}
